One exact and one random sampling method to assess the reliability of inferences from network enrichment analysis

### 2018-05-08 doc/genesetdp.tex
plots

\begin{figure}[htb]
	\begin{center}
    \begin{tabular}{c@{}c@{}c}
      \includegraphics[width=5cm]{figures/score_distribuition_Q10.png} &
      \includegraphics[width=5cm]{figures/score_distribuition_Q20.png} &
      \includegraphics[width=5cm]{figures/score_distribuition_Q30.png} \\
      $Q=10$ & $Q=20$ & $Q=30$ \\
    \end{tabular}
	\end{center}
  \caption{{\bf Score distribution of a query size of 10, 20 and 30 genes against the ``Glycolysis/Gluconeogenesis'' pathway.} GeneSetDP enables us to calculate the full score distribution for a query of a given size, $Q$, i.e. how many ways one can reach a certain score when adding up the scores for $Q$ genes.}
  \label{fig:score_dist}
\end{figure}

@@

\begin{figure}[htb]
  \begin{center}
      \includegraphics[width=1.0\textwidth]{figures/calibration_multiple.png}
	  % \includegraphics{figures/calibration_legend.png}
  \end{center}
  \caption{{\bf Calibration of GeneSetDP and GeneSetMC.} We selected 10000 random sets of 10, 20 and 30 genes from the investigated genome definition and calculated their $p$ values with GeneSetMC and GeneSetDP against the ``Glycolysis/Gluconeogenesis'' pathway. To test the $p$~values uniformity we plotted them against their {\em normalized rank}, i.e. each $p$~value's (<rank>-0.5)/<total number of $p$~values>. We also added the calibration curve of BinoX, evaluated on the same random sets. On all plots the dashed line shows $y = x$ and the dotted lines $y = 2x$ and $y = 0.5x$, for comparison}
  \label{fig:calibration}
\end{figure}

>>>>

\begin{figure}[htb]
	\begin{center}
		\includegraphics[width=1.0\textwidth]{figures/score_distribuition_multiple.png} 
    \end{center}
  \caption{{\bf Score distribution of a query size of 10, 20 and 30 genes against the ``Glycolysis/Gluconeogenesis'' pathway.} GeneSetDP enables us to calculate the full score distribution for a query of a given size, $Q$, i.e. how many ways one can reach a certain score when adding up the scores for $Q$ genes.}
  \label{fig:score_dist}
\end{figure}

@@

\begin{figure}[htb]
  \begin{center}
		\begin{tabular}[t]{c@{}c}
				\includegraphics[width=1.0\textwidth]{figures/calibration_multiple.png} &
				\includegraphics[width=0.2\textwidth]{figures/calibration_legend.png}
		\end{tabular}
  \end{center}
  \caption{{\bf Calibration of GeneSetDP and GeneSetMC.} We selected 10000 random sets of 10, 20 and 30 genes from the investigated genome definition and calculated their $p$ values with GeneSetMC and GeneSetDP against the ``Glycolysis/Gluconeogenesis'' pathway. To test the $p$~values uniformity we plotted them against their {\em normalized rank}, i.e. each $p$~value's (<rank>-0.5)/<total number of $p$~values>. We also added the calibration curve of BinoX, evaluated on the same random sets. On all plots the dashed line shows $y = x$ and the dotted lines $y = 2x$ and $y = 0.5x$, for comparison}
  \label{fig:calibration}
\end{figure}
